\documentclass[12pt]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{setspace}
\usepackage{titlesec}

% Professional styling
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setstretch{1.3}

\begin{document}

\begin{center}
    \LARGE \textbf{PROPERTY LISTING \& COMMISSION AGREEMENT} \\
    \vspace{0.8em}
    \normalsize Reference ID: \{\{ id \}\} \\
    Date of Agreement: \{\{ current\_date \}\}
\end{center}

\vspace{1.5em}

\section*{PREAMBLE}
This Property Listing and Commission Agreement ("Agreement") is entered into between \textbf{Property Express} ("Platform") and the Seller ("Seller"). By submitting the property details and digitally executing this document, the Seller agrees to be bound by the terms herein, enforceable under the laws of India.

\section*{PART I — SELLER IDENTIFICATION}
\begin{tabular}{ll}
Full Legal Name: & \{\{ sellerName \}\} \\
Email Address: & \{\{ sellerEmail \}\} \\
Phone Number: & \{\{ sellerPhone \}\} \\
Government ID: & \{\{ id \}\} \\
\end{tabular}

\vspace{1.5em}

\section*{PART II — PROPERTY SPECIFICATIONS}
\begin{tabular}{ll}
Property Title: & \{\{ propertyTitle \}\} \\
Property Type: & \{\{ propertyType \}\} \\
Full Address: & \{\{ address \}\} \\
General Location: & \{\{ location \}\} \\
Total Area: & \{\{ area \}\} sq.ft \\
Listed Sale Price: & INR \{\{ price \}\} \\
\end{tabular}

\vspace{1.5em}

\section*{PART III — TERMS AND CONDITIONS}

\textbf{Clause 1: Accuracy and Representation} \\
The Seller warrants that all property information provided is accurate and complete. Any material changes in property status must be reported to the Platform immediately.

\vspace{0.5em}

\textbf{Clause 2: Rights and Exclusivity} \\
The Seller grants Property Express the right to market the property through all its digital channels. The Seller confirms they have full legal authority to dispose of or lease the property.

\vspace{0.5em}

\textbf{Clause 3: Commission and Fees} \\
The Seller agrees to a success fee (commission) payable upon the execution of a sale or lease agreement with a lead provided by the Platform.

\section*{PART IV — EXECUTION AND SIGNATURES}
This document is digitally executed and timestamped.

\vspace{2em}

\begin{tabular}{ll}
Seller Signature: & \{\{ seller\_signature \}\} \\
Authorized Signatory: & \{\{ admin\_signature \}\} \\
Approval Date: & \{\{ current\_date \}\} \\
\end{tabular}

\vspace{2em}

\noindent \textit{This is a legally binding digital document. Property Express acts as a facilitating intermediary and is not liable for third-party legal disputes regarding property ownership.}

\end{document}
